Measuring causal influence with\\ back-to-back regression: the linear case

### 2019-05-23 paper/introduction.tex

Both forward and backward modeling have competing benefits and drawbacks. Specifically, forward modeling disentangles the independent contribution of collinear factors, but does not combine multidimensional observations. By contrast, backward modeling combines multiple observations, but does not disentangle collinear factors \citep{weichwald2015causal, hebart2018deconstructing, king2018encoding}.

>>>>

Both forward and backward modeling have competing benefits and drawbacks. Specifically, forward modeling disentangles the independent contribution of collinear factors, but does not combine multidimensional observations. By contrast, backward modeling combines multiple observations, but does not disentangle collinear factors \cite{weichwald2015causal, hebart2018deconstructing, king2018encoding}.
